Explore Vegetation Data

### 2015-06-30 explore_veg_data.Rmd
Added chunk to summarise the untagged species dbh by plot, species, year, and alive/dead status. Calculated counts, and average and total dbh

>>>>

Now I need to examine the data for alternate and non-host species DBH. These are the stems that are untagged and meet a 5cm DBH threshold.

```{r untagged species}
summary(alt_sp_dbh)
library(lubridate)
alt_sp_dbh$date <- as.Date(alt_sp_dbh$Date, format = "%m/%d/%Y")
filter(alt_sp_dbh, is.na(date)) # this should be 5/22/2012
alt_sp_dbh$Date[alt_sp_dbh$Date == ""] <- "5/22/2012 0:00:00"
alt_sp_dbh$date <- as.Date(alt_sp_dbh$Date, format = "%m/%d/%Y")
summary(alt_sp_dbh)
alt_sp_dbh$year <- year(alt_sp_dbh$date)
alt_sp_dbh <- alt_sp_dbh %>% select(-PlotVisit_PlotVisitID, -Date) %>% 
      rename(dbh = Measure)
unique(as.character(alt_sp_dbh$Species))

alt_sp_dbh$Species[alt_sp_dbh$Species == "PSME"] <- "psme"
alt_sp_dbh$Species <- tolower(alt_sp_dbh$Species)
summary(alt_sp_dbh)
unique(alt_sp_dbh$Species)
unique(alt_sp_dbh$Dead)
alt_sp_dbh$Dead <- ifelse(alt_sp_dbh$Dead == 0, "no", "yes")

alt_sp_live <- filter(alt_sp_dbh, Dead == "no")
alt_sp_dead <- filter(alt_sp_dbh, Dead == "yes")

alt_sp_summ <- left_join(
      # First data frame
      alt_sp_live %>% filter(year != 2012) %>% group_by(PlotID, Species, year) %>% 
      summarise(live_count = length(Species), live_avg_dbh = mean(dbh), live_tot_dbh = sum(dbh)),
      # Second data frame
      alt_sp_dead %>% filter(year != 2012) %>% group_by(PlotID, Species, year) %>% 
      summarise(dead_count = length(Species), dead_avg_dbh = mean(dbh), dead_tot_dbh = sum(dbh))
)

write.csv(alt_sp_summ, "analysis/data/untagged_dbh_summary.csv")
```
